\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[margin=1.3in]{geometry}

\author{Henry Yang : 19940503-1056}
\title{Wizard Of Wor \\\large a report for the course \\TDA572 (Game Engine Architectures)}
\date{Mars 2018}

\begin{document}
  \maketitle
  \section*{Abstract}
  \section{Introduction}

  This report is a report for the development of a clone of the 80's Arcade game \textbf{Wizard Of Wor}. The game said game, which this project is a clone of is an arcade game developed by Midway. This report will start by introducing the reader to the original Game, identifying the gameplay mechanics of the game, and other important key-features of this game.

  We will than go on and identifying the possible problems to be solved when creating a game like Wizard Of Wor and the solutions for these. In the same section, we will also discuss the viability of implementing all the possible features of this game. Since the there are many features in the said game, some of the features that are present in the original game will be omitted. This will be discussed here.

  The report will than go on to discuss the design the development process of the game, as well as challenges that surfaced during development. Additionally, this section will discuss the decision made regard the design and implementation of the features of the game.

  In the next section, the report will showcase, and discuss the results of the project. What could be done differently, future plans, and other discussions related to the project.

  The whole project is written in the language C++, which is a common language found within the area of Game development.

  The original game is playable by up to two people. The players are running around in a two dimensional maze with a lot of Monsters. The objective is to gather as much score as possible. Score points is acquired by killing the monsters in the Maze. In the case that two players are playing the game. The players can also gather points by killing each other.

  The players loses lives if they are killed by the monsters. From the beginning, each player starts with 3 lives. Monsters can kill the player by firing on them. The player will also lose a life if they collide with a monster.


\end{document}